---
title: "R Shiny Notebook"
output: html_notebook
---

```{r}
## Load Packages

sapply(c(
"gapminder", "ggforce", "gh", "globals", "openintro", "profvis",
"RSQLite", "shiny", "shinycssloaders", "shinyFeedback",
"shinythemes", "testthat", "thematic", "tidyverse", "vroom",
"waiter", "xml2", "zeallot", "lubridate", "reactable"
), require, character.only = TRUE)

```

## Chapter 1 Excercises
```{r 1-1}

ui <- fluidPage(
  numericInput("age", "How old are you?", value = NA),
  textInput("name", "What's your name?"),
  textOutput("greeting"),
  tableOutput("mortgage"),
  plotOutput("histogram")
  
)
server <- function(input, output, session) {
  output$histogram <- renderPlot({
    hist(rnorm(1000))
      }, res = 96)
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
shinyApp(ui, server)
```

```{r 1-2}

ui <- fluidPage(
  sliderInput("x", label = "If x is", min = 1, max = 50, value = 30),
  "then x times 5 is",
  textOutput("product")
)

server <- function(input, output, session) {
  output$product <- renderText({
    input$x * 5
  })
}

shinyApp(ui, server)

```

```{r 1-3}

ui <- fluidPage(
  sliderInput("x", label = "If x is", min = 1, max = 50, value = 30),
  sliderInput("y", label = "and y is", min = 1, max = 50, value = 30),
  "then, x times y is",
  textOutput("product")
)

server <- function(input, output, session) {
  output$product <- renderText({
    input$x * input$y
  })
}

shinyApp(ui, server)

```

```{r 1-4}

ui <- fluidPage(
  sliderInput("x", "If x is", min = 1, max = 50, value = 30),
  sliderInput("y", "and y is", min = 1, max = 50, value = 5),
  "then, (x * y) is", textOutput("product"),
  "and, (x * y) + 5 is", textOutput("product_plus5"),
  "and (x * y) + 10 is", textOutput("product_plus10")
)

server <- function(input, output, session) {
  product <- reactive({
    input$x * input$y
  })
  output$product <- renderText({
    product()
  })
  output$product_plus5 <- renderText({
    product() + 5
  })
  output$product_plus10 <- renderText({
    product() + 10
  })
}
shinyApp(ui, server)

```


```{r}

datasets <- c("economics", "faithfuld", "seals")
ui <- fluidPage(
  selectInput("dataset", "Dataset", choices = datasets),
  verbatimTextOutput("summary"),
  plotOutput("plot")
)

server <- function(input, output, session) {
  dataset <- reactive({
    get(input$dataset, "package:ggplot2")
  })
  output$summary <- renderPrint({
    summary(dataset())
  })
  output$plot <- renderPlot({
    plot(dataset())
    }, res = 96)
}
shinyApp(ui, server)

```


## Chapter 2 Basic UI

#### Free Text

Collect small amounts of text with textInput(), passwords with passwordInput(),
and paragraphs of text with textAreaInput():

#### Numeric Inputs

To collect numeric values, create a constrained text box with numericInput() or a
slider with sliderInput(). If you supply a length-2 numeric vector for the default
value of sliderInput(), you get a “range” slider with two ends

#### Dates

Collect a single day with dateInput() or a range of two days with dateRangeInput()

#### Limited Choices

There are two different approaches to allow the user to choose from a prespecified set
of options: selectInput() and radioButtons():

#### File Uploads

Allow the user to upload a file with fileInput()

#### Action Buttons

Let the user perform an action with actionButton() or actionLink()


```{r 2.1-1}

ui <- fluidPage(
  textInput("name", label = NULL, placeholder = "Your name", value = "")
)

shinyApp(ui, server)

```


```{r 2.1-2}

ui <- fluidPage(
  sliderInput("delivery", label = "When should we deliver?", value = ymd("2020-09-17"), min = ymd("2020-09-16"), max = ymd("2020-09-23"))
)

shinyApp(ui, server)


```

```{r 2.1-3}

ui <- fluidPage(
  sliderInput("range", label = "Choose a range", value = 50, min = 0, max = 100, step = 5,
              animate = TRUE)
)

shinyApp(ui, server)

```


```{r 2.1-4}
## Use choices

x <- list(Group1 = c(1,2,3,4,5), Group2 = c(4,5,6,7,8))

ui <- fluidPage(
  selectInput("num", label = "Choose a member from a group", choices = x)
)

shinyApp(ui, server)

```

### Outputs

#### Text

Output regular text with textOutput() and fixed width text (e.g., console output)
with verbatimTextOutput()

#### Tables

There are two options for displaying data frames in tables:

tableOutput() and renderTable()
These render a static table of data, showing all the data at once.

dataTableOutput() and renderDataTable()
These render a dynamic table, showing a fixed number of rows along with controls
to change which rows are visible.

#### Plots

You can display any type of R graphic with plotOutpu() and renderPlot()

#### Downloads

You can let the user download a file with downloadButton() or downloadLink().

```{r 2.2-1}

# a) User verbatimTextOutput()

# b) use textOutput()

# c) use verbatimTextOutput()

# d) verbatimTextOutput()

```

```{r 2.2-2}

ui <- fluidPage(
plotOutput("plot", width = "700px", height = "300px")
)
server <- function(input, output, session) {
output$plot <- renderPlot(plot(1:5), res = 96,
                          alt = "Scatterplot of five random numbers")
}


shinyApp(ui, server)
```

```{r 2.2-3}

ui <- fluidPage(
 dataTableOutput("table")
)
server <- function(input, output, session) {
  output$table <- renderDataTable(mtcars, options = list(pagelength = 5,
                                                         sorting = FALSE,
                                                         searching = FALSE))
}
shinyApp(ui, server)
```

```{r 2.2-4}

ui <- fluidPage(
  reactableOutput("table")
)
server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(mtcars, sortable = FALSE)
  })
}
shinyApp(ui, server)

```

## Chapter 3 Basic Reactivity

```{r}

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name, "!")
  })
}
shinyApp(ui,server)
```

#### Imperative vs Declarative Programming

Immperative programming

  Issue a specific command and it’s carried out immediately. This is the style of
  programming you’re used to in your analysis scripts: you command R to load
  your data, transform it, visualize it, and save the results to disk.
  
Declarative programming

  Express higher-level goals or describe important constraints, and rely on someone
  else to decide how and/or when to translate that into action. This is the style
  of programming you use in Shiny.
  
```{r 3.1-1}

server1 <- function(input, output, server) {
output$greeting <- renderText(paste0("Hello ", input$name))
}

server2 <- function(input, output, server) {
  greeting <- paste0("Hello ", input$name)
  output$greeting <- renderText(greeting())
}

server3 <- function(input, output, server) {
output$greting <- renderText(paste0("Hello", input$name))
}

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

server3 <- function(input, output, server) {
output$greting <- renderText(paste0("Hello", input$name))
}

shinyApp(ui,server)
```


```{r 3.1-2}

#server1 <- function(input, output, session) {
#  c <- reactive(input$a + input$b)
#  e <- reactive(c() + input$d)
#  output$f <- renderText(e())
#}

# input$a,input$b>>c>e>f

# input$d > e > f

#server2 <- function(input, output, session) {
#  x <- reactive(input$x1 + input$x2 + input$x3)
#  y <- reactive(input$y1 + input$y2)
#  output$z <- renderText(x() / y())
#}

# input$x1,input$x2,input$x3 > x > z

# input$y1,input$y2 > y > z

#server3 <- function(input, output, session) {
#  d <- reactive(c() ^ input$d)
#  a <- reactive(input$a * 10)
#  c <- reactive(b() / input$c)
#  b <- reactive(a() + input$b)
#}

# A > a > b > c > d

# B > b 

# C > c

# D > d

```


```{r 3.1-3}

# The code fails because we changed the range function to reactive call.
# Its bad practice to name reactives already existing function names



```

#### Reactive Expressions

