---
title: "R Shiny Notebook"
output: html_notebook
---

```{r}
## Load Packages

sapply(c(
"gapminder", "ggforce", "gh", "globals", "openintro", "profvis",
"RSQLite", "shiny", "shinycssloaders", "shinyFeedback",
"shinythemes", "testthat", "thematic", "tidyverse", "vroom",
"waiter", "xml2", "zeallot", "lubridate", "reactable"
), require, character.only = TRUE)

```

## Chapter 1 Excercises
```{r 1-1}

ui <- fluidPage(
  numericInput("age", "How old are you?", value = NA),
  textInput("name", "What's your name?"),
  textOutput("greeting"),
  tableOutput("mortgage"),
  plotOutput("histogram")
  
)
server <- function(input, output, session) {
  output$histogram <- renderPlot({
    hist(rnorm(1000))
      }, res = 96)
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}
shinyApp(ui, server)
```

```{r 1-2}

ui <- fluidPage(
  sliderInput("x", label = "If x is", min = 1, max = 50, value = 30),
  "then x times 5 is",
  textOutput("product")
)

server <- function(input, output, session) {
  output$product <- renderText({
    input$x * 5
  })
}

shinyApp(ui, server)

```

```{r 1-3}

ui <- fluidPage(
  sliderInput("x", label = "If x is", min = 1, max = 50, value = 30),
  sliderInput("y", label = "and y is", min = 1, max = 50, value = 30),
  "then, x times y is",
  textOutput("product")
)

server <- function(input, output, session) {
  output$product <- renderText({
    input$x * input$y
  })
}

shinyApp(ui, server)

```

```{r 1-4}

ui <- fluidPage(
  sliderInput("x", "If x is", min = 1, max = 50, value = 30),
  sliderInput("y", "and y is", min = 1, max = 50, value = 5),
  "then, (x * y) is", textOutput("product"),
  "and, (x * y) + 5 is", textOutput("product_plus5"),
  "and (x * y) + 10 is", textOutput("product_plus10")
)

server <- function(input, output, session) {
  product <- reactive({
    input$x * input$y
  })
  output$product <- renderText({
    product()
  })
  output$product_plus5 <- renderText({
    product() + 5
  })
  output$product_plus10 <- renderText({
    product() + 10
  })
}
shinyApp(ui, server)

```


```{r}

datasets <- c("economics", "faithfuld", "seals")
ui <- fluidPage(
  selectInput("dataset", "Dataset", choices = datasets),
  verbatimTextOutput("summary"),
  plotOutput("plot")
)

server <- function(input, output, session) {
  dataset <- reactive({
    get(input$dataset, "package:ggplot2")
  })
  output$summary <- renderPrint({
    summary(dataset())
  })
  output$plot <- renderPlot({
    plot(dataset())
    }, res = 96)
}
shinyApp(ui, server)

```


## Chapter 2 Basic UI

#### Free Text

Collect small amounts of text with textInput(), passwords with passwordInput(),
and paragraphs of text with textAreaInput():

#### Numeric Inputs

To collect numeric values, create a constrained text box with numericInput() or a
slider with sliderInput(). If you supply a length-2 numeric vector for the default
value of sliderInput(), you get a “range” slider with two ends

#### Dates

Collect a single day with dateInput() or a range of two days with dateRangeInput()

#### Limited Choices

There are two different approaches to allow the user to choose from a prespecified set
of options: selectInput() and radioButtons():

#### File Uploads

Allow the user to upload a file with fileInput()

#### Action Buttons

Let the user perform an action with actionButton() or actionLink()


```{r 2.1-1}

ui <- fluidPage(
  textInput("name", label = NULL, placeholder = "Your name", value = "")
)

shinyApp(ui, server)

```


```{r 2.1-2}

ui <- fluidPage(
  sliderInput("delivery", label = "When should we deliver?", value = ymd("2020-09-17"), min = ymd("2020-09-16"), max = ymd("2020-09-23"))
)

shinyApp(ui, server)


```

```{r 2.1-3}

ui <- fluidPage(
  sliderInput("range", label = "Choose a range", value = 50, min = 0, max = 100, step = 5,
              animate = TRUE)
)

shinyApp(ui, server)

```


```{r 2.1-4}
## Use choices

x <- list(Group1 = c(1,2,3,4,5), Group2 = c(4,5,6,7,8))

ui <- fluidPage(
  selectInput("num", label = "Choose a member from a group", choices = x)
)

shinyApp(ui, server)

```

### Outputs

#### Text

Output regular text with textOutput() and fixed width text (e.g., console output)
with verbatimTextOutput()

#### Tables

There are two options for displaying data frames in tables:

tableOutput() and renderTable()
These render a static table of data, showing all the data at once.

dataTableOutput() and renderDataTable()
These render a dynamic table, showing a fixed number of rows along with controls
to change which rows are visible.

#### Plots

You can display any type of R graphic with plotOutpu() and renderPlot()

#### Downloads

You can let the user download a file with downloadButton() or downloadLink().

```{r 2.2-1}

# a) User verbatimTextOutput()

# b) use textOutput()

# c) use verbatimTextOutput()

# d) verbatimTextOutput()

```

```{r 2.2-2}

ui <- fluidPage(
plotOutput("plot", width = "700px", height = "300px")
)
server <- function(input, output, session) {
output$plot <- renderPlot(plot(1:5), res = 96,
                          alt = "Scatterplot of five random numbers")
}


shinyApp(ui, server)
```

```{r 2.2-3}

ui <- fluidPage(
 dataTableOutput("table")
)
server <- function(input, output, session) {
  output$table <- renderDataTable(mtcars, options = list(pagelength = 5,
                                                         sorting = FALSE,
                                                         searching = FALSE))
}
shinyApp(ui, server)
```

```{r 2.2-4}

ui <- fluidPage(
  reactableOutput("table")
)
server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(mtcars, sortable = FALSE)
  })
}
shinyApp(ui, server)

```

## Chapter 3 Basic Reactivity

```{r}

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
server <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name, "!")
  })
}
shinyApp(ui,server)
```

#### Imperative vs Declarative Programming

Immperative programming

  Issue a specific command and it’s carried out immediately. This is the style of
  programming you’re used to in your analysis scripts: you command R to load
  your data, transform it, visualize it, and save the results to disk.
  
Declarative programming

  Express higher-level goals or describe important constraints, and rely on someone
  else to decide how and/or when to translate that into action. This is the style
  of programming you use in Shiny.
  
```{r 3.1-1}

server1 <- function(input, output, server) {
output$greeting <- renderText(paste0("Hello ", input$name))
}

server2 <- function(input, output, server) {
  greeting <- paste0("Hello ", input$name)
  output$greeting <- renderText(greeting())
}

server3 <- function(input, output, server) {
output$greting <- renderText(paste0("Hello", input$name))
}

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

server3 <- function(input, output, server) {
output$greting <- renderText(paste0("Hello", input$name))
}

shinyApp(ui,server)
```


```{r 3.1-2}

#server1 <- function(input, output, session) {
#  c <- reactive(input$a + input$b)
#  e <- reactive(c() + input$d)
#  output$f <- renderText(e())
#}

# input$a,input$b>>c>e>f

# input$d > e > f

#server2 <- function(input, output, session) {
#  x <- reactive(input$x1 + input$x2 + input$x3)
#  y <- reactive(input$y1 + input$y2)
#  output$z <- renderText(x() / y())
#}

# input$x1,input$x2,input$x3 > x > z

# input$y1,input$y2 > y > z

#server3 <- function(input, output, session) {
#  d <- reactive(c() ^ input$d)
#  a <- reactive(input$a * 10)
#  c <- reactive(b() / input$c)
#  b <- reactive(a() + input$b)
#}

# A > a > b > c > d

# B > b 

# C > c

# D > d

```


```{r 3.1-3}

# The code fails because we changed the range function to reactive call.
# Its bad practice to name reactives already existing function names



```

#### Reactive Expressions

```{r}
library(ggplot2)
freqpoly <- function(x1, x2, binwidth = 0.1, xlim = c(-3, 3)) {
df <- data.frame(
    x = c(x1, x2),
    g = c(rep("x1", length(x1)), rep("x2", length(x2)))
  )
  ggplot(df, aes(x, colour = g)) +
    geom_freqpoly(binwidth = binwidth, size = 1) +
    coord_cartesian(xlim = xlim)
}

t_test <- function(x1, x2) {
  test <- t.test(x1, x2)
  #  use sprintf() to format t.test() results compactly
    sprintf(
      "p value: %0.3f\n[%0.2f, %0.2f]",
      test$p.value, test$conf.int[1], test$conf.int[2]
   )
}

x1 <- rnorm(100, mean = 0, sd = 0.5)
x2 <- rnorm(200, mean = 0.15, sd = 0.9)

freqpoly(x1, x2)
cat(t_test(x1, x2))

```

```{r}
ui <- fluidPage(
  fluidRow(
    column(4,
      "Distribution 1",
      numericInput("n1", label = "n", value = 1000, min = 1),
      numericInput("mean1", label = "μ", value = 0, step = 0.1),
      numericInput("sd1", label = "σ", value = 0.5, min = 0.1, step = 0.1)
    ),
    column(4,
      "Distribution 2",
      numericInput("n2", label = "n", value = 1000, min = 1),
      numericInput("mean2", label = "μ", value = 0, step = 0.1),
      numericInput("sd2", label = "σ", value = 0.5, min = 0.1, step = 0.1)
    ),
    column(4,
      "Frequency polygon",
      numericInput("binwidth", label = "Bin width", value = 0.1, step = 0.1),
      sliderInput("range", label = "range", value = c(-3, 3), min = -5, max = 5)
    )
  ),
  fluidRow(
    column(9, plotOutput("hist")),
    column(3, verbatimTextOutput("ttest"))
  )
)

server <- function(input, output, session) {
  output$hist <- renderPlot({
    x1 <- rnorm(input$n1, input$mean1, input$sd1)
    x2 <- rnorm(input$n2, input$mean2, input$sd2)
    freqpoly(x1, x2, binwidth = input$binwidth, xlim = input$range)
  }, res = 96)
  
  output$ttest <- renderText({
    x1 <- rnorm(input$n1, input$mean1, input$sd1)
    x2 <- rnorm(input$n2, input$mean2, input$sd2)
    
    t_test(x1, x2)
  })
}
shinyApp(ui,server)
```


#### Controlling Timing of Evaluation

```{r}

### Using a timer

ui <- fluidPage(
  fluidRow(
    column(3,
      numericInput("lambda1", label = "lambda1", value = 3),
      numericInput("lambda2", label = "lambda2", value = 5),
      numericInput("n", label = "n", value = 1e4, min = 0)
    ),
    column(9, plotOutput("hist"))
  )
)

server <- function(input, output, session) {
  timer <- reactiveTimer(500)
  x1 <- reactive({
    timer()
    rpois(input$n, input$lambda1)
  })
  x2 <- reactive({
    timer()
    rpois(input$n, input$lambda2)
  })
  
  output$hist <- renderPlot({
    freqpoly(x1(), x2(), binwidth = 1, xlim = c(0, 40))
  }, res = 96)
}  
shinyApp(ui,server)
```

```{r}
### On click

ui <- fluidPage(
  fluidRow(
    column(3,
      numericInput("lambda1", label = "lambda1", value = 3),
      numericInput("lambda2", label = "lambda2", value = 5),
      numericInput("n", label = "n", value = 1e4, min = 0),
      actionButton("simulate", "Simulate!")
    ),
    column(9, plotOutput("hist"))
  )
)

server <- function(input, output, session) {
  x1 <- eventReactive(input$simulate, {
    rpois(input$n, input$lambda1)
  })
  x2 <- eventReactive(input$simulate, {
    rpois(input$n, input$lambda2)
  })
  output$hist <- renderPlot({
    freqpoly(x1(), x2(), binwidth = 1, xlim = c(0, 40))
  }, res = 96)
}

shinyApp(ui,server)
```

#### Observers

```{r}

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

server <- function(input, output, session) {
  string <- reactive(paste0("Hello ", input$name, "!"))
  output$greeting <- renderText(string())
  observeEvent(input$name, {
    message("Greeting performed")
  })
}
shinyApp(ui,server)
```

## Chapter 4 Case Study: ER Injuries

```{r}

### Downloading dataset neiss
dir.create("neiss")
#> Warning in dir.create("neiss"): 'neiss' already exists
download <- function(name) {
  url <- "https://raw.githubusercontent.com/hadley/mastering-shiny/main/neiss/"
  download.file(paste0(url, name), paste0("neiss/", name), quiet = TRUE)
}
download("injuries.tsv.gz")
download("population.tsv")
download("products.tsv")

injuries <- vroom::vroom("neiss/injuries.tsv.gz")
injuries %>% glimpse()
products <- vroom::vroom("neiss/products.tsv")
products %>% glimpse()
population <- vroom::vroom("neiss/population.tsv")
population %>% glimpse()
```

##### Exploration

```{r}

selected <- injuries %>% filter(prod_code == 649)
nrow(selected)

selected %>% count(location, wt = weight, sort = T)

selected %>% count(body_part, wt = weight, sort = T)

selected %>% count(diag, wt = weight, sort = T)

summary <- selected %>%
  count(age, sex, wt = weight)
summary

summary %>%
  ggplot(aes(x = age, y = n, color = sex)) +
  geom_line()
```


```{r}

summary <- selected %>%
  count(age, sex, wt = weight) %>%
  left_join(population, by = c("age", "sex")) %>%
  mutate(rate = n / population * 1e4)

summary %>%
  ggplot(aes(age, rate, colour = sex)) +
  geom_line(na.rm = TRUE) +
  labs(y = "Injuries per 10,000 people")

selected %>%
  sample_n(10) %>%
  select(narrative)
```

#### Prototype

```{r}
prod_codes <- setNames(products$prod_code, products$title)

ui <- fluidPage(
  fluidRow(
    column(8,
      selectInput("code", "Product",
      choices = setNames(products$prod_code, products$title),
      width = "100%"
      )
    ),
    column(2, selectInput("y", "Y axis", c("rate", "count")))
  ),
  fluidRow(
    column(4, tableOutput("diag")),
    column(4, tableOutput("body_part")),
    column(4, tableOutput("location"))
  ),
  fluidRow(
    column(12, plotOutput("age_sex"))
  ),
  fluidRow(
    column(2, actionButton("story", "Tell me a story")),
    column(10, textOutput("narrative"))
  )
)

server <- function(input, output, session) {
  
  selected <- reactive(injuries %>% filter(prod_code == input$code))

  output$diag <- renderTable(count_top(selected(), diag), width = "100%")

  output$body_part <- renderTable(count_top(selected(), body_part), width = "100%")

  output$location <- renderTable(count_top(selected(), location), width = "100%")
  
  summary <- reactive({
    selected() %>%
      count(age, sex, wt = weight) %>%
      left_join(population, by = c("age", "sex")) %>%
      mutate(rate = n / population * 1e4)
  })
  
  output$age_sex <- renderPlot({
    if (input$y == "count") {
      summary() %>%
        ggplot(aes(age, n, colour = sex)) +
        geom_line() +
        labs(y = "Estimated number of injuries")
    } else {
      summary() %>%
        ggplot(aes(age, rate, colour = sex)) +
        geom_line(na.rm = TRUE) +
        labs(y = "Estimated number of injuries/10,000")
    }
  }, res = 96)
  
  narrative_sample <- eventReactive(
    list(input$story, selected()),
    selected() %>% pull(narrative) %>% sample(1)
  )
  output$narrative <- renderText(narrative_sample())

}

shinyApp(ui,server)
```

#### Polish Tables

```{r}
### Truncate tables

injuries %>%
  mutate(diag = fct_lump(fct_infreq(diag), n = 5)) %>%
  group_by(diag) %>%
  summarise(n = as.integer(sum(weight)))

count_top <- function(df, var, n = 5) {
  df %>%
    mutate({{ var }} := fct_lump(fct_infreq({{ var }}), n = n)) %>%
    group_by({{ var }}) %>%
    summarise(n = as.integer(sum(weight)))
}
```

#### Narrative


Chapter 4 Excercises

```{r 4.1-1}
## Not included

```

```{r 4.1-2}

# fct_infreq orders diag by their count.

# applying lump after infreq takes all the diag values after the nth most
# common and lumps them into 'Other' as the last factor level

# applying lump first will simply Order the first n factors alphabetically and
# sum the remaining factors into 'Other'. Applying fct_infreq() after this
# will reorder according to freq, of which 'Other' was the largest here.

```

```{r 4.1-3}
prod_codes <- setNames(products$prod_code, products$title)

ui <- fluidPage(
  fluidRow(
    column(8,
      selectInput("code", "Product",
      choices = setNames(products$prod_code, products$title),
      width = "100%"
      )
    ),
    column(2, selectInput("y", "Y axis", c("rate", "count"))),
    column(2, numericInput("rows", "Rows", min = 1, max = 10, value = 5)),
  ),
  fluidRow(
    column(4, tableOutput("diag")),
    column(4, tableOutput("body_part")),
    column(4, tableOutput("location"))
  ),
  fluidRow(
    column(12, plotOutput("age_sex"))
  ),
  fluidRow(
    column(2, actionButton("story", "Tell me a story")),
    column(10, textOutput("narrative"))
  )
)

server <- function(input, output, session) {
  
  selected <- reactive(injuries %>% filter(prod_code == input$code))

  output$diag <- renderTable(count_top(selected(), diag, n = input$rows-1), width = "100%")

  output$body_part <- renderTable(count_top(selected(), body_part, n = input$rows-1), width = "100%")

  output$location <- renderTable(count_top(selected(), location, n = input$rows-1), width = "100%")
  
  summary <- reactive({
    selected() %>%
      count(age, sex, wt = weight) %>%
      left_join(population, by = c("age", "sex")) %>%
      mutate(rate = n / population * 1e4)
  })
  
  output$age_sex <- renderPlot({
    if (input$y == "count") {
      summary() %>%
        ggplot(aes(age, n, colour = sex)) +
        geom_line() +
        labs(y = "Estimated number of injuries")
    } else {
      summary() %>%
        ggplot(aes(age, rate, colour = sex)) +
        geom_line(na.rm = TRUE) +
        labs(y = "Estimated number of injuries/10,000")
    }
  }, res = 96)
  
  narrative_sample <- eventReactive(
    list(input$story, selected()),
    selected() %>% pull(narrative) %>% sample(1)
  )
  output$narrative <- renderText(narrative_sample())

}

shinyApp(ui,server)



```

```{r 4.1-4}

prod_codes <- setNames(products$prod_code, products$title)

ui <- fluidPage(
  fluidRow(
    column(8,
      selectInput("code", "Product",
      choices = setNames(products$prod_code, products$title),
      width = "100%"
      )
    ),
    column(2, selectInput("y", "Y axis", c("rate", "count"))),
    column(2, numericInput("rows", "Rows", min = 1, max = 10, value = 5)),
  ),
  fluidRow(
    column(4, tableOutput("diag")),
    column(4, tableOutput("body_part")),
    column(4, tableOutput("location"))
  ),
  fluidRow(
    column(12, plotOutput("age_sex"))
  ),
  fluidRow(
    column(1, actionButton("back_story","Back")),
    column(1, actionButton("next_story", "Next")),
    column(10, textOutput("narrative"))
  )
)

server <- function(input, output, session) {
  
  selected <- reactive(injuries %>% filter(prod_code == input$code))
  
  ## Find max number of rows
  
  max_no_rows <-reactive(max(length(unique(selected()$diag)),
                    length(unique(selected()$body_part)),
                    length(unique(selected()$location))))
  
  observeEvent(input$code, {
    updateNumericInput(session, "rows", max = max_no_rows())
  })
  
  table_rows <- reactive(input$rows-1)

  output$diag <- renderTable(count_top(selected(), diag, n = table_rows()), width = "100%")

  output$body_part <- renderTable(count_top(selected(), body_part, n = table_rows()), width = "100%")

  output$location <- renderTable(count_top(selected(), location, n = table_rows()), width = "100%")
  
  summary <- reactive({
    selected() %>%
      count(age, sex, wt = weight) %>%
      left_join(population, by = c("age", "sex")) %>%
      mutate(rate = n / population * 1e4)
  })
  
  output$age_sex <- renderPlot({
    if (input$y == "count") {
      summary() %>%
        ggplot(aes(age, n, colour = sex)) +
        geom_line() +
        labs(y = "Estimated number of injuries")
    } else {
      summary() %>%
        ggplot(aes(age, rate, colour = sex)) +
        geom_line(na.rm = TRUE) +
        labs(y = "Estimated number of injuries/10,000")
    }
  }, res = 96)
  
  story <- reactiveVal(1)
  
  max_no_story <- reactive(max(length(selected()$narrative)))
  
  observeEvent(input$code, story(1))
  
  observeEvent(input$next_story, {
    story((story() %% max_no_story()) + 1)
  })
  
  observeEvent(input$back_story, {
    story((story() %% max_no_story()) -1)
  })
  
  output$narrative <- renderText(selected()$narrative[story()])

}

shinyApp(ui,server)

```

## Shiny Workflow

### Development Workflow

#### Creating the App

```{r}

library(shiny)

ui <- fluidPage(
)

server <- function(input, output, session) {
}

shinyApp(ui, server)

```


```{r}

f <- function(x) g(x)
g <- function(x) h(x)
h <- function(x) x * 2
ui <- fluidPage(
selectInput("n", "N", 1:10),
plotOutput("plot")
)
server <- function(input, output, session) {
output$plot <- renderPlot({
n <- f(input$n)
plot(head(cars, n))
}, res = 96)
}
shinyApp(ui, server)

```

### Layout, HTML, Themes. Chapter 6

```{r 6.1-1}
### sidebarpanel by default gives mainpanel 2/3 of the width or 8 columns in
## fluidRow using column sizes.
```


```{r 6.1-2}
ui <- fluidPage(
  titlePanel("Central limit theorem"),
  sidebarLayout(
    mainPanel(
    plotOutput("hist")
    ),
    sidebarPanel(
    numericInput("m", "Number of samples:", 2, min = 1, max = 100)
    )
  )
)

server <- function(input, output, session) {
  output$hist <- renderPlot({
    means <- replicate(1e4, mean(runif(input$m)))
    hist(means, breaks = 20)
  }, res = 96)
}

shinyApp(ui,server)
```

```{r 6.1-3}
library(shiny)

ui <- fluidPage(
 tags$p(
  "You made ",
  tags$b("$", textOutput("amount", inline = FALSE)),
  " in the last ",
  textOutput("days", inline = TRUE),
  " days "
  )
)

shinyApp(ui, server)

```

#### Multiple Layouts


#### Themes

```{r 6.3-1}

theme <- bs_theme(bg = 'pink', fg = 'green', primary = 'orange')
bs_theme_preview(theme)

```

#### Under the Hood

## Graphics, Chapter 7

```{r}

ui <- fluidPage(
  plotOutput("plot", brush = "plot_brush"),
  tableOutput("data")
)

server <- function(input, output, session) {
  output$plot <- renderPlot({
    ggplot(mtcars, aes(wt, mpg)) + geom_point()
  }, res = 96)
  output$data <- renderTable({
    brushedPoints(mtcars, input$plot_brush)
  })
}
shinyApp(ui,server)
```

```{r}

set.seed(1014)

df <- data.frame(x = rnorm(100), y = rnorm(100))

ui <- fluidPage(
  plotOutput("plot", click = "plot_click", )
)
server <- function(input, output, session) {
  
  dist <- reactiveVal(rep(1, nrow(df)))
  
  observeEvent(input$plot_click,
    dist(nearPoints(df, input$plot_click, allRows = TRUE, addDist = TRUE)$dist_)
  )
  
  output$plot <- renderPlot({
    df$dist <- dist()
    ggplot(df, aes(x, y, size = dist)) +
    geom_point() +
    scale_size_area(limits = c(0, 1000), max_size = 10, guide = NULL)
  }, res = 96)
}
shinyApp(ui,server)
```

```{r}

ui <- fluidPage(
  plotOutput("plot", brush = "plot_brush", dblclick = "plot_reset")
)

server <- function(input, output, session) {
  selected <- reactiveVal(rep(FALSE, nrow(mtcars)))
  
  observeEvent(input$plot_brush, {
    brushed <- brushedPoints(mtcars, input$plot_brush, allRows =      TRUE)$selected_
    selected(brushed | selected())
  })
  
  observeEvent(input$plot_reset, {
    selected(rep(FALSE, nrow(mtcars)))
  })
  
  output$plot <- renderPlot({
    mtcars$sel <- selected()
    ggplot(mtcars, aes(wt, mpg)) +
    geom_point(aes(colour = sel))
  }, res = 96)
}

shinyApp(ui,server)
```

```{r}

ui <- fluidPage(
  sliderInput("height", "height", min = 100, max = 500, value =     250),
  sliderInput("width", "width", min = 100, max = 500, value =       250),
  plotOutput("plot", width = 250, height = 250)

)
server <- function(input, output, session) {
  output$plot <- renderPlot(
    width = function() input$width,
    height = function() input$height,
    res = 96,
    {
      plot(rnorm(20), rnorm(20))
    }
  )
}

```

#### Validation and Notification

```{r}

ui <- fluidPage(
  shinyFeedback::useShinyFeedback(),
  textInput("dataset", "Dataset name"),
  tableOutput("data")
)

server <- function(input, output, session) {
  data <- reactive({
    req(input$dataset)
    exists <- exists(input$dataset, "package:datasets")
    shinyFeedback::feedbackDanger("dataset", !exists, "Unknown dataset")
    req(exists, cancelOutput = TRUE)
    get(input$dataset, "package:datasets")
  })
  
output$data <- renderTable({
  head(data())
})
}

shinyApp(ui,server)
```


```{r}

ui <- fluidPage(
  numericInput("x", "x", value = 0),
  selectInput("trans", "transformation",
    choices = c("square", "log", "square-root")
  ),
  textOutput("out")
)

server <- function(input, output, server) {
  output$out <- renderText({
    if (input$x < 0 && input$trans %in% c("log", "square-root")) {
      validate("x can not be negative for this transformation")
    }
    switch(input$trans,
      square = input$x ^ 2,
      "square-root" = sqrt(input$x),
      log = log(input$x)
    )
  })
}

shinyApp(ui,server)
```

```{r}

ui <- fluidPage(
  actionButton("goodnight", "Good night")

)

server <- function(input, output, session) {
  data <- reactive({
    id <- showNotification("Reading data...", duration = NULL, closeButton = FALSE)
    on.exit(removeNotification(id), add = TRUE)
    read.csv(input$file$datapath)
  })
}

shinyApp(ui,server)

```

#### Progressive Updates

```{r}

ui <- fluidPage(
  tableOutput("data")
)

server <- function(input, output, session) {
  
notify <- function(msg, id = NULL) {
  showNotification(msg, id = id, duration = NULL, closeButton = FALSE)
  }
  
data <- reactive({
  id <- notify("Reading data...")
    on.exit(removeNotification(id), add = TRUE)
    Sys.sleep(1)
    notify("Reticulating splines...", id = id)
    Sys.sleep(1)
    notify("Herding llamas...", id = id)
    Sys.sleep(1)
    notify("Orthogonalizing matrices...", id = id)
    Sys.sleep(1)
    mtcars
  })
  output$data <- renderTable(head(data()))
}

shinyApp(ui,server)
```

#### Progress Bars

```{r}

ui <- fluidPage(
  waiter::use_waitress(),
  numericInput("steps", "How many steps?", 10),
  actionButton("go", "go"),
  textOutput("result")
)

server <- function(input, output, session) {
  data <- eventReactive(input$go, {
    waitress <- waiter::Waitress$new(max = input$steps)
    on.exit(waitress$close())
    
    for (i in seq_len(input$steps)) {
      Sys.sleep(0.5)
      waitress$inc(1)
    }
    runif(1)
})
  
output$result <- renderText(round(data(), 2))

}
shinyApp(ui,server)
```

#### Confirming and Undoing


```{r}

ui <- fluidPage(
  actionButton("delete", "Delete all files?")
)

server <- function(input, output, session) {
  observeEvent(input$delete, {
    showModal(modal_confirm)
  })
  
  observeEvent(input$ok, {
    showNotification("Files deleted")
    removeModal()
  })
  observeEvent(input$cancel, {
    removeModal()
  })
}

shinyApp(ui,server)

```

#### Undoing an Action

```{r}

ui <- fluidPage(
  textAreaInput("message",
    label = NULL,
    placeholder = "What's happening?",
    rows = 3
  ),
  actionButton("tweet", "Tweet")
)

runLater <- function(action, seconds = 3) {
  observeEvent(
    invalidateLater(seconds * 1000), action,
    ignoreInit = TRUE,
    once = TRUE,
    ignoreNULL = FALSE,
    autoDestroy = FALSE
  )
}

server <- function(input, output, session) {
  waiting <- NULL
  last_message <- NULL
  
  observeEvent(input$tweet, {
    notification <- glue::glue("Tweeted '{input$message}'")
    last_message <<- input$message
    updateTextAreaInput(session, "message", value = "")
    
    showNotification(
      notification,
      action = actionButton("undo", "Undo?"),
      duration = NULL,
      closeButton = FALSE,
      id = "tweeted",
      type = "warning"
    )
    
    waiting <<- runLater({
      cat("Actually sending tweet...\n")
      removeNotification("tweeted")
    })
  })
  
  observeEvent(input$undo, {
    waiting$destroy()
    showNotification("Tweet retracted", id = "tweeted")
    updateTextAreaInput(session, "message", value = last_message)
  })
}
shinyApp(ui,server)
```

### Uploads and Downloads Chapter 9

#### Upload


```{r}

ui <- fluidPage(
  fileInput("file", NULL, accept = c(".csv", ".tsv")),
  numericInput("n", "Rows", value = 5, min = 1, step = 1),
  tableOutput("head")
)

server <- function(input, output, session) {
  data <- reactive({
    req(input$file)
    ext <- tools::file_ext(input$file$name)
    switch(ext,
      csv = vroom::vroom(input$file$datapath, delim = ","),
      tsv = vroom::vroom(input$file$datapath, delim = "\t"),
      validate("Invalid file; Please upload a .csv or .tsv file")
    )
  })
  output$head <- renderTable({
    head(data(), input$n)
  })
}
shinyApp(ui,server)

```

#### Download

```{r}

ui <- fluidPage(
  selectInput("dataset", "Pick a dataset", ls("package:datasets")),
  tableOutput("preview"),
  downloadButton("download", "Download .tsv")
)

server <- function(input, output, session) {
  data <- reactive({
    out <- get(input$dataset, "package:datasets")
    if (!is.data.frame(out)) {
      validate(paste0("'", input$dataset, "' is not a data frame"))
    }
    out
  })
  
  output$preview <- renderTable({
    head(data())
  })
  output$download <- downloadHandler(
    filename = function() {
      paste0(input$dataset, ".tsv")
    },
    content = function(file) {
      vroom::vroom_write(data(), file)
    }
  )
}
shinyApp(ui,server)
```

#### Downloading Reports

```{r}

report_path <- tempfile(fileext = ".Rmd")
file.copy("report.Rmd", report_path, overwrite = TRUE)

ui <- fluidPage(
  sliderInput("n", "Number of points", 1, 100, 50),
  downloadButton("report", "Generate report")
)

render_report <- function(input, output, params) {
  rmarkdown::render(input,
    output_file = output,
    params = params,
    envir = new.env(parent = globalenv())
  )
}

server <- function(input, output, session) {
  output$report <- downloadHandler(
    filename = "report.html",
    content = function(file) {
      params <- list(n = input$n)
      callr::r(
        render_report,
        list(input = report_path, output = file, params = params)
      )
    }
  )
}

shinyApp(ui,server)

```


#### Case Study

```{r}
ui_upload <- sidebarLayout(
  sidebarPanel(
    fileInput("file", "Data", buttonLabel = "Upload..."),
    textInput("delim", "Delimiter (leave blank to guess)", ""),
    numericInput("skip", "Rows to skip", 0, min = 0),
    numericInput("rows", "Rows to preview", 10, min = 1)
  ),
  mainPanel(
    h3("Raw data"),
    tableOutput("preview1")
  )
)

ui_clean <- sidebarLayout(
  sidebarPanel(
    checkboxInput("snake", "Rename columns to snake case?"),
    checkboxInput("constant", "Remove constant columns?"),
    checkboxInput("empty", "Remove empty cols?")
  ),
  mainPanel(
    h3("Cleaner data"),
  tableOutput("preview2")
  )
)

ui_download <- fluidRow(
  column(width = 12, downloadButton("download", class = "btn-block"))
)

ui <- fluidPage(
  ui_upload,
  ui_clean,
  ui_download
)

server <- function(input, output, session) {
# Upload ---------------------------------------------------------
  raw <- reactive({
    req(input$file)
    delim <- if (input$delim == "") NULL else input$delim
    vroom::vroom(input$file$datapath, delim = delim, skip = input$skip)
  })
  
  output$preview1 <- renderTable(head(raw(), input$rows))
# Clean ----------------------------------------------------------
cleaned_names <- reactive({
  out <- raw()
  if (input$snake) {
    names(out) <- janitor::make_clean_names(names(out))
  }
  out
})

remove_empty <- reactive({
  out <- cleaned_names()
  if (input$empty) {
    out <- janitor::remove_empty(out, "cols")
  }
  out
})

remove_constant <- reactive({
  out <- remove_empty()
  if (input$constant) {
    out <- janitor::remove_constant(out)
  }
  out
})

  output$preview2 <- renderTable(head(remove_constant(), input$rows))
# Download -------------------------------------------------------
  output$download <- downloadHandler(
    filename = function() {
      paste0(tools::file_path_sans_ext(input$file$name), ".tsv")
    },
    content = function(file) {
      vroom::vroom_write(remove_constant(), file)
    }
  )
}
shinyApp(ui,server)
```

#### Excercises Chapter 9

```{r 9.1-1}

noise <- noise_worley(c(100,100))
plot(as.raster(normalize(noise)))
# Export and save as image.


```


```{r 9.1-2}

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Data", buttonLabel = "Upload..."),
      selectInput("variable", "Variable to test", choices = c(""))
    ),
    mainPanel(
      verbatimTextOutput("results")
    )
  )
)

server <- function(input, output, session) {
  data <- reactive({
    req(input$file)
    vroom::vroom(input$file$datapath, delim = ",")
  })
  observeEvent(input$file, {
    updateSelectInput(inputId = "variable", choices = names(data()))
  })
  output$results <- renderPrint(
    t.test(data()[input$variable])
  )
  
}
shinyApp(ui,server)
```

```{r 9.1-3}
library(shiny)
library(tidyverse)
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Data", buttonLabel = "Upload..."),
      selectInput("variable", "Variable to plot", choices = c("")),
      downloadButton("downloadpng",label = "Download PNG", class = "btn-block"),
      downloadButton("downloadpdf",label = "Download PDF", class = "btn-block"),
      downloadButton("downloadjpeg",label = "Download JPEG", class = "btn-block")
    ),
    mainPanel(
      plotOutput("hist")
    )
  )
)

server <- function(input, output, session) {
  data <- reactive({
    req(input$file)
    vroom::vroom(input$file$datapath, delim = ",")
  })
  observeEvent(input$file, {
    updateSelectInput(inputId = "variable", choices = names(data()))
  })
  
  plot <- reactive({
    ggplot(data()) +
      geom_histogram(aes_string(input$variable))
  })
  
  output$hist <- renderPlot(
    plot()
  )
  
  output$downloadpng <- downloadHandler(
    filename = "Shinyplot.png",
    content = function(file) {
        png(file)
        print(plot())
        dev.off()
      }
  )
  output$downloadpdf <- downloadHandler(
    filename = "Shinyplot.pdf",
    content = function(file) {
        pdf(file)
        print(plot())
        dev.off()
      }
  )
  output$downloadjpeg <- downloadHandler(
    filename = "Shinyplot.jpeg",
    content = function(file) {
        jpeg(file)
        print(plot())
        dev.off()
      }
  )
}
shinyApp(ui,server)
```


```{r 9.1-4}
library(brickr)
library(png)
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Image", buttonLabel = "Upload..."),
      downloadButton("download",label = "Download Image", class = "btn-block")
    ),
    mainPanel(
      plotOutput("mosaic")
    )
  )
)

server <- function(input, output, session) {
  img <- reactive({
    req(input$file)
    png::readPNG(input$file$datapath)
  })
  
  image <- reactive({
    img() %>% 
      image_to_mosaic(img_size = 36) %>%
      build_mosaic()
  })
  
  output$mosaic <- renderPlot({
    image()
  }
  )
  
  output$download <- downloadHandler(
    filename = "Legomosaic.png",
    content = function(file) {
        png(file)
        print(image())
        dev.off()
      }
  )
}
shinyApp(ui,server)
```

```{r}

cleaned_names <- reactive({
  out <- raw()
  if (input$snake) {
    names(out) <- janitor::make_clean_names(names(out))
  }
  out
})

remove_empty <- reactive({ 
  if (input$empty) {
    out <- janitor::remove_empty(cleaned_names(), "cols")
  }
  out
})
remove_constant <- reactive({
  if (input$constant) {
    out <- janitor::remove_constant(remove_empty())
  }
  out
})


```

### Dynamic UI Chapter 10

#### Updating Inputs

```{r}

ui <- fluidPage(
  numericInput("min", "Minimum", 0),
  numericInput("max", "Maximum", 3),
  sliderInput("n", "n", min = 0, max = 3, value = 1)
)

server <- function(input, output, session) {
  observeEvent(input$min, {
    updateSliderInput(inputId = "n", min = input$min)
  })
  observeEvent(input$max, {
    updateSliderInput(inputId = "n", max = input$max)
  })
}

```

